### 2023-09-22 README.rmd
removing vignettes from CRAN release. They will be only available on the website now
edit for publication in JOSS

<!-- badges: start -->
[![R-CMD-check](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml)
```{r echo=FALSE, results='asis'}
cat(
  badge_github_version(color = "green"),
  badge_cran_release(color = "blue"),
  badge_cran_download(color = "blue", type = "grand-total")
)
```
[![Codecov test coverage](https://codecov.io/gh/JeremyGelb/geocmeans/branch/master/graph/badge.svg)](https://app.codecov.io/gh/JeremyGelb/geocmeans?branch=master)
<!-- badges: end -->

@@

`geocmeans` version 0.3.2 is licensed under [GPL2 License](https://github.com/JeremyGelb/geocmeans/blob/master/LICENSE.txt).

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml)
```{r echo=FALSE, results='asis'}
cat(
  badge_github_version(color = "green"),
  badge_cran_release(color = "blue"),
  badge_cran_download(color = "blue", type = "grand-total")
)
```
[![Codecov test coverage](https://codecov.io/gh/JeremyGelb/geocmeans/branch/master/graph/badge.svg)](https://app.codecov.io/gh/JeremyGelb/geocmeans?branch=master)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.8316593.svg)](https://doi.org/10.5281/zenodo.8316593)

<!-- badges: end -->

@@

`geocmeans` version 0.3.4 is licensed under [GPL2 License](https://github.com/JeremyGelb/geocmeans/blob/master/LICENSE.txt).
